Since XMPP is a decentralized protocol, you'll need a server before you can get started using it.
If you're just interested in chatting, you may want to set up an account at a public XMPP service,
such as one of the services listed here:

\url{http://xmpp.org/services}

(Unfortunately, services I have used in the past or currently use, such as core.im and talkr.im, are
not listed here.  But they're still worth taking a look at.)

An alternative to registering at a public XMPP service is to host your own.  This is useful if you want
full control of your data or your server, or if you want your server to be internally visible only.

There are several implementations of XMPP servers out there, a (fairly) comprehensive list can be found
here:

\url{http://xmpp.org/xmpp-software/servers/}

I'll be demonstrating Prosody in this presentation, since that is the XMPP server with which I am most
familiar.  Two other servers of note are djabberd (noteworthy because it is written in Perl, but it
doesn't look very active) and ejabberd (which is written in Erlang, but is noteworthy because of its
popularity and wide availability of extensions).

You can get Prosody from here: \url{http://prosody.im/}

I have a Prosody server running on my laptop right now, if you'd like to follow along, feel free to connect to my ad-hoc
network and create an account.  The domain name for the server is \textbf{chat.madmongers}.  The configuration syntax for Prosody is
fairly simple (it's just Lua), and you don't usually need to deviate much from the configuration provided in the distribution to
get up and running, but for the sake of brevity, I've omitted the configuration file from the presentation itself.  If you'd
like to take a look at the configuration I'm using, you can take a look here:

\example{prosody.cfg.lua}
