\documentclass{article}

\usepackage[display]{texpower}
\usepackage[landscape]{geometry}
\usepackage{hyperref}

\pagestyle{empty}

\begin{document}

\begin{titlepage}
\vspace*{\fill}
\begin{center}
{\huge \bfseries An Introduction to XMPP} \\[0.5cm]
{\LARGE Madison Perl Mongers} \\[0.5cm]
{\large Rob Hoelz (\href{mailto:rob@hoelz.ro}{rob@hoelz.ro})} \\[0.5cm]
{\large December 2010}
\end{center}
\vspace*{\fill}
\end{titlepage}

\newpage
\part{Introduction}

\newpage
What is XMPP?

\newpage
XMPP stands for e\textbf{X}tensible \textbf{M}essaging and \textbf{P}resence \textbf{P}rotocol.

\newpage
For those of you not familiar with it, XMPP (also known as Jabber) is a near-realtime
protocol used for instant messaging.

\newpage
However, chat is not the only thing you can use it for!

\newpage
\part{Setup}

\newpage
This section will cover some of the open-source XMPP servers, and
how to set one up.  In this talk, we'll be using Prosody (\url{http://prosody.im}).

\newpage
\part{Concepts}

\newpage
This section will cover some basic concepts in XMPP.  Highly abstract; little to no
actual code.

\begin{itemize}
\item JIDs
\item Domains vs Hosts
\item Types of Stanzas
\end{itemize}

\newpage
\part{Clients}

\newpage
This section covers the various clients available for different operating systems.
\url{http://xmpp.org/xmpp-software/clients}

\newpage
\part{Client Libraries}

\newpage
There are many open-source implementations of XMPP out there; for a comprehensive list,
please consult \url{http://xmpp.org/xmpp-software/libraries}.

\newpage
Since this is a MadMongers meeting, we'll be covering AnyEvent::XMPP.

\newpage
But before we dive into that, I should probably plug Strophe.

\newpage
Strophe is a Javascript library that allows web applications to speak XMPP.

\newpage
\part{Miscellanea}

\newpage
This section contains stuff I want to mention, but I haven't found a place for.
This section will not exist in the final draft.

\newpage
\begin{itemize}
\item XEPs (and the general extensibility of XMPP)
\item Service Discovery? (and disco)
\item MUC
\item PubSub
\item BOSH
\item Sending binary data across XMPP
\end{itemize}

\newpage

\vspace*{\fill}
\begin{center}
\textbf{\Huge Questions?}
\end{center}
\vspace*{\fill}

\newpage
\appendix
\section{Resources}

\end{document}
